# Exploring Sample Metadata

## Load required libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
knitr::opts_chunk$set(comment = NA)
```


## Read size
The size of the reads can tell us how big is the dataset and can help to estimate the computational needs.

Top five smallest project by read size
```{r}
read_csv("results/read_size_asc.csv", show_col_types = FALSE) %>% 
head(5)
```

Top five biggest project by read size
```{r}
read_csv("results/read_size_desc.csv", show_col_types = FALSE) %>% 
head(5)
```

## Compare read size by BioProject

![](figures/read_size.svg)

<br>

## Read size by variables within a project

![](figures/PRJNA477349_read_size.svg)

<br>

![](figures/PRJNA208226_read_size.svg)

<br>

# Interactive Sample Location Map

In this section, an interactive map is provided to explore sample locations based on their coordinates. Dropping pins on the map is possible if you have coordinate data, such as latitudes and longitudes of collection points. The pins represent different projects, and by hovering over a pin, you will be able to see information about the corresponding project.</p><p>It is a good practice during sample collection to take the coordinates for plotting location points, which will add clarity to the report. For the interactive experience, view this report in a browser that supports JavaScript. You can also zoom-in or out for better exploration.

```{r echo=FALSE, results='asis'}
library(htmltools)

HTML('<iframe src="map/sample_gps.html" width="800" height="600"></iframe>')

```

